---
title: "chapter3"
author: "Hsiang-Leng, Wang"
date: "2019/11/22"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# MOOC Introduction to Open Data Science 2019: Homework3
## Step1. Check the data

#### Read the joined student alcohol consumption data as alc dataset

```{r}
alc <- read.table("http://s3.amazonaws.com/assets.datacamp.com/production/course_2218/datasets/alc.txt", sep=",", header=TRUE)
```

#### Summary the alc dataset
```{r}
str(alc)
```
The dataset alc includes 35 varibles with 382 rows. The alc_use is the average of column Dalc and Walc (weekday and weekend alcohol consumption). If the average alcohol consumption is higher than 2, it is regarded as high alcohol usage student which is shown in column 'high_use' as TRUE.

#### Choose four interesting variables in alc dataset
Personally, I think alcohol consumption is related to a person's relationship with family members, higher alcohol concumption may caused by bad relationship, so I select #24 famrel as one onf the analysis target. In addition, in my opinion, if a student tends to have a promising future, he/she may focus on study more rather than be absent in class too often, so I select #14 studytime and #30 absences as the interesing variables. Last, I am interested in if the score is related to alcohol consumption, so I choose #32 G3 as the fourth variable.

>
- #14 studytime - weekly study time (numeric: 1 - <2 hours, 2 - 2 to 5 hours, 3 - 5 to 10 hours, or 4 - >10 hours) 
- #24 famrel - quality of family relationships (numeric: from 1 - very bad to 5 - excellent)
- #30 absences - number of school absences (numeric: from 0 to 93) 
- #32 G3 - final grade (numeric: from 0 to 20, output target)

```{r}
library(magrittr) # needs to be run every time you start R and want to use %>%
library(dplyr)
alc_4 <- alc %>% select(16, 24, 30, 33, 34, 35)
head(alc_4, n=10)
```

#### Graphically explore: a) cross-tabulations b) scatter plots
##### a) cross-tabulations
high_use vs studytime
```{r}
alc_4.v1 <- table(alc$high_use, alc$studytime)
round(prop.table(alc_4.v1,1), 2)
```
high_use vs famrel
```{r}
alc_4.v2 <- table(alc$high_use, alc$famrel)
round(prop.table(alc_4.v2,1), 2)
```
high_use vs absences
```{r}
alc_4.v3 <- table(alc$high_use, alc$absences)
round(prop.table(alc_4.v3,1), 2)
```
high_use vs G3
```{r}
alc_4.v4 <- table(alc$high_use, alc$G3)
round(prop.table(alc_4.v4,1), 2)
```
##### b) scatter plots

```{r, echo = FALSE}
# access the GGally and ggplot2 libraries
library(GGally)
library(ggplot2)
# [-1] excludes the last column (high_use)
pairs(alc_4[-6], col = alc_4$high_use)
p <- ggpairs(alc_4, mapping = aes(), lower = list(combo = wrap("facethist", bins = 20)))
p
```
